---
title: "tf-idf"
author: "Nick Rhodes"
date: "29 May 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
works <- readRDS("dickens.RDS")
```

# Analysing the works of Dickens

## 1. Word-document frequency


```{r frequency, echo=FALSE}
book_words <- works %>%
  unnest_tokens(word, text) %>%
  count(title, word, sort = TRUE)

total_words <- book_words %>% 
  group_by(title) %>% 
  summarize(total = sum(n))

book_words <- left_join(book_words, total_words)

print(book_words)

ggplot(book_words, aes(n/total, fill = title)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~title, ncol = 2, scales = "free_y")
```

## 2. Zipf's Law

Zipf's law states that the frequency that a word appears is inversely proportional to its rank.

```{r zipf, echo=FALSE}
freq_by_rank <- book_words %>% 
  group_by(title) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total)

freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = title)) + 
  geom_abline(intercept = -0.62, slope = -1.1, color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()
```
## 3. tf-idf

The idea of tf-idf is to find the important words for the content of each document by decreasing the weight for commonly used words and increasing the weight for words that are not used very much in a collection or corpus of documents, in this case, the works of Dickens as a whole. Calculating tf-idf attempts to find the words that are important (i.e., common) in a text, but not too common.

```{r tf_idf, echo=FALSE}
book_words <- book_words %>%
  bind_tf_idf(word, title, n)

book_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(title) %>% 
  top_n(10) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = title)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~title, ncol = 3, scales = "free") +
  coord_flip()
```
